Deadlock Freedom on Self-Assembled DNA Nano Networks

### 2013-11-05 trunk/PAPER/introduction.tex
Removed figure/text overlapping

\begin{figure}
\centering
\begin{tabular}{cc}
    \includegraphics[width=0.40\textwidth]{pictures/dna2b.eps} &
    \includegraphics[width=0.40\textwidth]{pictures/dna1_complex2.eps} \\
 (a) & (b)
 \end{tabular}
  \caption{DNA tag matching and Resulting Irregualr Topology}
  \label{fig:nana}
\end{figure}
These aspects of a DNA-self assembly process lead to some important
implications to be addressed when approaching to the design of
computer architecture: a computational model should be based on a
distributed network of small computing and storage nodes, randomly
placed and interconnected (see Figure~\ref{fig:nana}).
Proof-of-concept of such kind of computational model can be found for
example in~\cite{patwardhan2006_1}.  Since no regularity can be
assumed in such network, a topology agnostic strategy that avoids
deadlock should be adopted in order to route packets (e.g.
instructions and data operands) among nodes.  It is important to
underline that, altougth we can assume an architecture similar to the
one depicted in Figure~\ref{fig:nana} as background, the topology discovery
problem faced in this work is more general and not strictly dependent on any of the
underlying computing architecture.

>>>>

\begin{figure*}
\centering
\begin{tabular}{cc}
    \includegraphics[width=0.40\textwidth]{pictures/dna2b.eps} &
    \includegraphics[width=0.40\textwidth]{pictures/dna1_complex2.eps} \\
 (a) & (b)
 \end{tabular}
  \caption{DNA tag matching and Resulting Irregualr Topology}
  \label{fig:nana}
\end{figure*}
These aspects of a DNA-self assembly process lead to some important
implications to be addressed when approaching to the design of
computer architecture: a computational model should be based on a
distributed network of small computing and storage nodes, randomly
placed and interconnected (see Figure~\ref{fig:nana}).
Proof-of-concept of such kind of computational model can be found for
example in~\cite{patwardhan2006_1}.  Since no regularity can be
assumed in such network, a topology agnostic strategy that avoids
deadlock should be adopted in order to route packets (e.g.
instructions and data operands) among nodes.  It is important to
underline that, altougth we can assume an architecture similar to the
one depicted in Figure~\ref{fig:nana} as background, the topology discovery
problem faced in this work is more general and not strictly dependent on any of the
underlying computing architecture.
